Numerical simulation and entropy dissipative cure of the carbuncle instability for the shallow water circular hydraulic jump

### 2021-03-07 numerics_paper/version2/numerical_chj.tex
more changes

Next we briefly review two commonly-used Riemann solvers: those of Rusanov and
Roe.  We refer to \cite{ketcheson2020riemann} and references therein for
a detailed description of these two Riemann solvers in the context of
the shallow water equations.
Neither of these solvers deals with the carbuncle instability in a fully
satisfactory way.  Rusanov's solver suppresses the carbuncle but 
(unless the mesh is highly refined)
is known to
also suppress related real instabilities, while Roe's solver exhibits carbuncles.
Later we will combine these two solvers in order to better deal with shock instability.
Both of these solvers satisfy the conservation property
\begin{align} \label{rs_conservation}
    \amdq_\imh + \apdq_\imh = \bff(\bfq_i) - \bff(\bfq_{i-1}).
\end{align}

>>>>

Next we briefly review two commonly-used Riemann solvers: those of Rusanov and
Roe.  We refer to \cite{ketcheson2020riemann} and references therein for
a detailed description of these two Riemann solvers in the context of
the shallow water equations.
Neither of these solvers deals with the carbuncle instability in a fully
satisfactory way.  
Rusanov's solver suppresses the carbuncle instability but may 
introduce excessive numerical dissipation, while Roe's solver exhibits carbuncles.
Later we will combine these two solvers in order to better deal with shock instability.
Both of these solvers satisfy the conservation property
\begin{align} \label{rs_conservation}
    \amdq_\imh + \apdq_\imh = \bff(\bfq_i) - \bff(\bfq_{i-1}).
\end{align}
